method

### 2022-06-20 06_Paper/ER-ED/method.Rmd
added utility ratings

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
$$
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
$$ 
Level-1-predictors will be centered within cluster[@Enders2007].
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).

>>>>

To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
$$
\begin{split}
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
\end{split}
$$ 
Level-1-predictors will be centered within cluster[@Enders2007].
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).
